Query Optimization for Dynamic Imputation

### 2017-02-28 paper/experiments.tex
Remove fcc references

\subsubsection{freeCodeCamp 2016 New Coder Survey}
For our second set of experiments, we chose to use data collected
by freeCodeCamp as a part of a survey of new software developers
(both professional and amateur)~\cite{fcc-data}. freeCodeCamp is an open-source
community that helps users learn how to program. Their \textit{2016 New Coder Survey} consists of responses by over 15,000 people to 48 different
demographic and programming-related questions.
The survey targeted users who were related to coding organizations.

We use a version of the data that has been pre-processed, but where missing values remain.
For example, 46.6\% of entries for entry \textit{commutetime} are missing. However, it is worth noting that some of the missing values
are also expected, given the way the data has been de-normalized. For example, \textit{bootcamploanyesno}, a binary attribute encoding
whether a respondent had a loan for a bootcamp, is expected to be null for participants who did not attend a bootcamp.

We chose a subset of 17 attributes, shown in~\Cref{table:fcc-description}, along with the percentage of missing values.

@@

\subsubsection{American Community Survey}
For our final experiment, we introduce a simple aggregate query over data from the American Community Survey (ACS), which
provides a number of public data sets collected by the U.S. Census Bureau.
We used a cleaned version of the 2012 Public Use Microdata Sample (PUMS) data kindly provided by the authors of~\cite{akande2015empirical}.
Given that the data had been cleaned, we artificially dirtied it by removing 40\% of the values uniformly at random.
The final dataset consists of 671,153 rows and 37 integer columns.

\subsection{Queries}
We collected a set of queries (\Cref{fig:queries}) that we think are interesting to plan.
We believe that they could reasonably be written by a user in the course of data analysis.

@@

Our first set of queries is on the CDC data (\Cref{fig:queries-cdc}). In~\Cref{q1}, we
calculate the average cuff size for users based on their income data. In~\Cref{q2}, we compare
creatine levels for individuals with low, medium, and high incomes spectrum and above a
certain weight. In~\Cref{q3}, we extract the average blood lead levels for children under
the age of 6 years. In~\Cref{q4}, we calculate the average systolic blood pressure, by
gender, for subjects with a body mass index indicating obesity.

>>>>

\subsubsection{freeCodeCamp 2016 New Coder Survey}
For our second set of experiments, we use data collected by freeCodeCamp, an open-source
community for learning to code, as a part of a survey of new software
developers~\cite{fcc-data}.  The \textit{2016 New Coder Survey} consists of responses by
over 15,000 people to 48 different demographic and programming-related questions.  The
survey targeted users who were related to coding organizations.

We use a version of the data that has been pre-processed, but where missing values remain.
For example, 46.6\% of \textit{commutetime} responses are missing. However, it is worth
noting that some of the missing values are also expected, given the way the data has been
de-normalized. For example, \textit{bootcamploanyesno}, a binary attribute encoding whether
a respondent had a loan for a bootcamp, is expected to be null for participants who did not
attend a bootcamp.

We choose a subset of 17 attributes, which are shown in~\Cref{table:fcc-description} along
with the percentage of missing values.

@@

\subsubsection{American Community Survey}
For our final experiment, we run a simple aggregate query over data from the American
Community Survey (ACS), a comprehensive survey conducted by the U.S.
Census Bureau. We use a cleaned version of the 2012 Public Use Microdata Sample (PUMS)
data kindly provided by the authors of~\cite{akande2015empirical}. Given that the data had
been cleaned, we artificially dirtied it by removing 40\% of the values uniformly at random.
The final dataset consists of 671,153 rows and 37 integer columns.

\subsection{Queries}
We collect a set of queries (\Cref{fig:queries}) that we think are interesting to plan.
We believe that they could reasonably be written by a user in the course of data analysis.

@@

Our first set of queries is on the CDC data (\Cref{fig:queries-cdc}).
\Cref{q1} calculates calculate the average cuff size for users based on their income data.
\Cref{q2} compares creatine levels for individuals with low, medium, and high incomes spectrum and above a certain weight.
\Cref{q3} extracts the average blood lead levels for children under the age of 6 years.
\Cref{q4} calculates the average systolic blood pressure, by gender, for subjects with a body mass index indicating obesity.
